---
title: "overlap_connectivity"
output: html_notebook
---

#Import libraries and dataset
```{r}
library(readxl)
library(ggplot2)
library(data.table)
library('gmodels')
library(svglite)
toverlap_import <- read_excel("IN_overlap_connect.xlsx")
```

#Analysis of FS
Plot boxplot of overlap scores for different connection groups. Fig 2E
```{r}
toverlap = toverlap_import[toverlap_import$subtype == "FS",]

bp<-ggplot(toverlap,aes(x=connectivity, y=overlap))+
  geom_boxplot()+ylab("FS axonal overlap score")
bp
```

Plot fraction of pairs with high vs low overlap, and inhibition vs no inhibition. Fig 2F
```{r}
#set overlap threshold
toverlap$high <- toverlap$overlap>0.1

#fraction of excitatory pairs (high vs low overlap)
mytable <- table(toverlap$excitation,toverlap$high)
mytable
fisher.test(mytable)

relfreq <- data.table(mytable)
bp <- ggplot(relfreq, aes(x=V2, y=N, fill=V1)) +
      geom_bar(width=1,stat="identity",position = 'fill')+
  xlab("Overlap > 0.1")+ylab("FS relative fraction")+
  scale_fill_brewer(palette="Reds")
bp

#fraction of reciprocal pairs (high vs low overlap)
mytable <- table(toverlap$reciprocity,toverlap$high)
mytable
fisher.test(mytable)

relfreq <- data.table(mytable)
bp <- ggplot(relfreq, aes(x=V2, y=N, fill=V1)) +
      geom_bar(width=1,stat="identity",position = 'fill')+
  xlab("Overlap > 0.1")+ylab("FS relative fraction")+
  scale_fill_brewer(palette="PuRd")
bp

#fraction of excitatory pairs (with vs without inhibition)
mytable <- table(toverlap$excitation,toverlap$inhibition)
mytable
fisher.test(mytable)

relfreq <- data.table(mytable)
bp <- ggplot(relfreq, aes(x=V2, y=N, fill=V1)) +
      geom_bar(width=1,stat="identity",position = 'fill')+
  xlab("inhibition")+ylab("FS relative fraction")+
  scale_fill_brewer(palette="Reds")
bp

#fraction of reciprocal pairs (with vs without inhibition)
mytable <- table(toverlap$reciprocity,toverlap$inhibition)
mytable
fisher.test(mytable)

relfreq <- data.table(mytable)
bp <- ggplot(relfreq, aes(x=V2, y=N, fill=V1)) +
      geom_bar(width=1,stat="identity",position = 'fill')+
  xlab("inhibition")+ylab("FS relative fraction")+
  scale_fill_brewer(palette="PuRd")
bp
```

#Repeat analysis for NFS 
Plot boxplot of overlap scores for different connection groups. Fig S2B
```{r}
toverlap = toverlap_import[toverlap_import$subtype == "NFS",]

bp<-ggplot(toverlap,aes(x=connectivity, y=overlap))+
  geom_boxplot()+ylab("NFS axonal overlap score")
bp
```

Plot fraction of pairs with high vs low overlap, and inhibition vs no inhibition. Fig S2C
```{r}
#set overlap threshold
toverlap$high <- toverlap$overlap>0.1

#fraction of excitatory pairs (high vs low overlap)
mytable <- table(toverlap$excitation,toverlap$high)
mytable
fisher.test(mytable)

relfreq <- data.table(mytable)
bp <- ggplot(relfreq, aes(x=V2, y=N, fill=V1)) +
      geom_bar(width=1,stat="identity",position = 'fill')+
  xlab("Overlap > 0.1")+ylab("NFS relative fraction")+
  scale_fill_brewer(palette="Reds")
bp

#fraction of reciprocal pairs (high vs low overlap)
mytable <- table(toverlap$reciprocity,toverlap$high)
mytable
fisher.test(mytable)

relfreq <- data.table(mytable)
bp <- ggplot(relfreq, aes(x=V2, y=N, fill=V1)) +
      geom_bar(width=1,stat="identity",position = 'fill')+
  xlab("Overlap > 0.1")+ylab("NFS relative fraction")+
  scale_fill_brewer(palette="PuRd")
bp

#fraction of excitatory pairs (with vs without inhibition)
mytable <- table(toverlap$excitation,toverlap$inhibition)
mytable
fisher.test(mytable)

relfreq <- data.table(mytable)
bp <- ggplot(relfreq, aes(x=V2, y=N, fill=V1)) +
      geom_bar(width=1,stat="identity",position = 'fill')+
  xlab("inhibition")+ylab("NFS relative fraction")+
  scale_fill_brewer(palette="Reds")
bp

#fraction of reciprocal pairs (with vs without inhibition)
mytable <- table(toverlap$reciprocity,toverlap$inhibition)
mytable
fisher.test(mytable)

relfreq <- data.table(mytable)
bp <- ggplot(relfreq, aes(x=V2, y=N, fill=V1)) +
      geom_bar(width=1,stat="identity",position = 'fill')+
  xlab("inhibition")+ylab("NFS relative fraction")+
  scale_fill_brewer(palette="PuRd")
bp
```